Normalized expressions

### 2021-08-09 analysis/normalized.Rmd
New tags for normalized expressions

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_expr = expr_expression,
    expr_resolved,
    func = expr_resolved_function, # the function (if any) at the root of the AST of expr_resolved
    parsed = expr_parsed_expression,
    hash = expr_resolved_hash,
    match.call = expr_match_call,
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes,
    n_op = interp_eval,
    envir = envir_expression,
    caller_srcref,
    caller_expression,
    environment_class
  ) -> E

@@

  E_cano %>% write_fst(min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz, lock_path)
}

@@

@@

```{r}
nb_mf_match.call <- modelframes %>% filter(!is.na(match.call)) %>% pull(src_ref) %>% n_distinct()
```

@@

```{r}
match.call_df <- E_cano %>% filter(!is.na(match.call))

@@

```{r, eval=dataset_name == "package"}
manual_value_necessary <- read_csv(path(params$base_dir, "non-necessary-value-evals.csv"), col_types = cols(src_ref = col_character(), necessary = col_logical()))

>>>>

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  #base_dir: Data/package/
  base_dir: /mnt/ocfs_vol_00/project-evalr/evalr-experiment/run/preprocess/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_expr = expr_expression,
    expr_resolved,
    func = expr_resolved_function, # the function (if any) at the root of the AST of expr_resolved
    #parsed = expr_parsed_expression,
    hash = expr_resolved_hash,
    #match.call = expr_match_call,
    arg_size = expr_resolved_length, #   Size in characters of argument 
    ast_nodes = expr_resolved_nodes,
    n_op = interp_eval,
    envir = envir_expression,
    caller_srcref,
    caller_expression,
    environment_class
  ) -> E

@@

  #E_cano %>% write_fst(min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  #write.fst(sz, lock_path)
}

@@

```{r}
simple_minimized <- E_cano %>% filter(type != "bytecode") %>%
  mutate(minimized = if_else(minimized == "<-", "<", minimized)) %>%
  group_by(src_ref) %>%
  filter(all(minimized %in% c("X", "V", "$", "<"))) %>%
  summarise(minimized = paste0(sort(unique(minimized)), collapse = ""), length = str_length(minimized))

simple_minimized_one <- simple_minimized %>% filter(length == 1) %>% nrow()
simple_minimized_more <- simple_minimized %>% filter(length > 1) %>% nrow()

r("nb simple minimized one", simple_minimized_one)
r("nb simple minimized more", simple_minimized_more)
```

@@

```{r}
#no more match.call column
#nb_mf_match.call <- modelframes %>% filter(!is.na(match.call)) %>% pull(src_ref) %>% n_distinct()
nb_mf_match.call <- modelframes
```

@@

```{r}
# No more match.call column
#match.call_df <- E_cano %>% filter(!is.na(match.call))
match.call_df <- E_cano

@@

```{r, eval=dataset_name == "package", eval = FALSE}
manual_value_necessary <- read_csv(path(params$base_dir, "non-necessary-value-evals.csv"), col_types = cols(src_ref = col_character(), necessary = col_logical()))
